\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-05-25 paper/subdocuments/introduction.Rnw
fixed path

<<Swiss inequality from other studies>>=
library(ggplot2)
library(reshape)
number_ticks <- function(n) {function(limits) pretty(limits, n)}
swissGini_long<-melt(swissGini,id="Year")
ggplot(data=swissGini_long,
  aes(y=value,x=Year),shape=variable)+
  ylab("Gini") +
  scale_y_continuous(limits=c(0.18,0.4)) +
  scale_x_continuous(limits=c(1982,2012),breaks=number_ticks(10)) +
  geom_point(aes(shape=variable),size=3)+
  geom_line(data=swissGini_long[!is.na(swissGini_long$value),],aes(linetype=variable))+
  theme_bw()
@

% Darauf verweisen, dass der Trend eher abwärts weist bzw. auf Stabilität. Aber auch darauf hinweisen, dass eine lange und konsistente Zeitreihe nicht vorliegt.

@@

% Albeit the awarness of an assessment of income and wealth simuntanously is rising, we focus in this paper on income inequality, which is  know as the core driver of economic inequlity
% Dann lassen sich einige Passagen streichen. Man könnte auch auf verschiedene Publikationen verweisen, welche die Bedeutung von Vermögen untersuchen -> Buch von Piketty, Müller und Schoch und dann aber ziemlich schnell darauf verweisen, dass wir uns hier auf Einkommen konzentrieren.
% Auch erste Dell Studie erwähnen -> es hat Zahlen zur Schweiz. Auch Probleme erwähnen (Fehlende Informationen zu Altersvorsorgevermögen -> hat aber niemand eine Lösung bisher.)
% Studies on inequality have to adress several thorny challenges. One has to define the centrale measure of inequality and find adquate data. Recent studies accentuate the importance of a broader concept of economic wellbeeing including measures for income, consumption and wealth alike. But each area is confronted with own measurement problems. Measure of consumptions are largely missing in tax data, albeit deductions can be understood as mandatory consumptions somehow. Measures of wealth are included in tax data, but are not connectable to the respctive income and therefore can only be analyzed separate. In danger of falling a pittraps it seems appriate to move in small steps. Therefore we focus our analysis on income, which is undoubtly a crucial indicator of economic wellbeeing.
% Also the Federal Statistical Office is increasing their effort to get sound data concering the distribution of wealth vgl. Müller und Schoch (2014).

>>>>

<<Swiss inequality Plot>>=
library(ggplot2)
library(foreign)
number_ticks <- function(n) {function(limits) pretty(limits, n)}
swissGini<-read.csv("../../data/swissGini.csv",header=TRUE,sep=";")
ggplot(swissGini, aes(x=Year,y=LIS))+
  geom_line(aes(x=Year,y=LIS))+
  geom_point(aes(x=Year,y=LIS),size=3.5)+
  xlab("Year") +
  scale_x_continuous(breaks=number_ticks(10))+
  ylab("Gini") +
  scale_y_continuous(limits=c(0,0.5)) +
  theme_bw()
@

@@

% Albeit the awarness of an assessment of income and wealth simuntanously is rising, we focus in this paper on income inequality, which is the know as the core driver of economic inequlity
% Dann lassen sich einige Passagen streichen. Man könnte auch auf verschiedene Publikationen verweisen, welche die Bedeutung von Vermögen untersuchen -> Buch von Piketty, Müller und Schoch und dann aber ziemlich schnell darauf verweisen, dass wir uns hier auf Einkommen konzentrieren.
% Auch erste Dell Studie erwähnen -> es hat Zahlen zur Schweiz. Auch Probleme erwähnen (Fehlende Informationen zu Altersvorsorgevermögen -> hat aber niemand eine Lösung bisher.)
% Studies on inequality have to adress several thorny challenges. One has to define the centrale measure of inequality and find adquate data. Recent studies accentuate the importance of a broader concept of economic wellbeeing including measures for income, consumption and wealth alike. But each area is confronted with own measurement problems. Measure of consumptions are largely missing in tax data, albeit deductions can be understood as mandatory consumptions somehow. Measures of wealth are included in tax data, but are not connectable to the respctive income and therefore can only be analyzed separate. In danger of falling a pittraps it seems appriate to move in small steps. Therefore we focus our analysis on income, which is undoubtly a crucial indicator of economic wellbeeing.
% Also the Federal Statistical Office is increasing their effort to get sound data concering the distribution of wealth vgl. Müller und Schoch (2014).
